Real Estate

### 2022-11-08 src/real_estate.Rmd
add column for median rent

```{r}
# add MSA_median rent data
MSA_realEstate_compiled<- MSA_median_rent_data %>% 
  select(cbsa, rent50_1) %>%
  mutate(rent50_1 = as.numeric(rent50_1)) %>% 
  left_join(MSA_realEstate_data) %>% 
  left_join(MSA_demographics)
```

```{r}
# combine real estate and demographic data by cbsa
MSA_RE_ratios <- MSA_realEstate_compiled %>% 
      # calculate income to home price
  mutate(income_to_homeprice = median_income_usd_2021/house_price_2021) %>% 
  # calculate rent to income ratio
  mutate(avg_rent_to_income = avg_rent_2021/median_income_usd_2021) %>% 
  mutate(med_rent_to_income = rent50_1/median_income_usd_2021)

>>>>

```{r}
# add MSA_median rent data
MSA_realEstate_compiled<- MSA_median_rent_data %>% 
  select(cbsa, rent50_0) %>%
  mutate(median_rent = as.numeric(rent50_0)) %>% 
  left_join(MSA_realEstate_data) %>% 
  left_join(MSA_demographics)
```

```{r}
# combine real estate and demographic data by cbsa
MSA_RE_ratios <- MSA_realEstate_compiled %>% 
      # calculate income to home price
  mutate(income_to_homeprice = median_income_usd_2021/house_price_2021) %>% 
  # calculate rent to income ratio
  mutate(avg_rent_to_income = avg_rent_2021/median_income_usd_2021) %>% 
  mutate(med_rent_to_income = median_rent/median_income_usd_2021)
